On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2020-11-18 paper/cav_determinisim_main.tex
Changed format to fit ITS guidlines

% ***************************************************
%  TITLE
% ***************************************************
\title{On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification}
% \title{On the Precision of Game Engines used for Simulation-based Autonomous Vehicle Verification}
\author[1,3]{Abanoub Ghobrial\thanks{$^{1}${\footnotesize \{abanoub.ghobrial, greg.chance, kevin.mcareavey, kerstin.eder\}@bristol.ac.uk}}}
\author[1,3]{Greg Chance}
\author[1,3]{Kevin McAreavey}
\author[2,3]{Severin Lemaignan\thanks{$^{2}${\footnotesize \{severin.lemaignan, tony.pipe\}@brl.ac.uk}}}
\author[2,3]{Tony Pipe}
\author[1,3]{Kerstin Eder}
\affil[1]{Trustworthy Systems Laboratory, University of Bristol, Bristol, UK}
\affil[2]{University of West of England, Bristol, UK}
\affil[3]{Bristol Robotics Laboratory, Bristol, UK}
\maketitle

\begin{abstract}
\noindent 
Game engines are increasingly used as simulation platforms by the autonomous vehicle (AV) community to develop vehicle control systems and test environments.
%
A key requirement for simulation-based development and verification is determinism.
%
Whereby, a deterministic process will always produce the same output given the same initial conditions and event history.
%
Thus, making tests repeatable and yielding simulation results that are trustworthy and straightforward to debug.
%
However, game engines are seldom deterministic.

@@

% ***************************************************
%  FUNDING, REFS
% ***************************************************
\section*{Acknowledgements}
This research has in part been funded by the ROBOPILOT and CAPRI projects. Both
projects are part-funded by the Centre for Connected and Autonomous
Vehicles (CCAV), delivered in partnership with Innovate UK under grant numbers
103703 (CAPRI) and 103288 (ROBOPILOT), respectively.
\printbibliography

>>>>

% ***************************************************
%  TITLE
% ***************************************************
\title{On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification}
% \title{On the Precision of Game Engines used for Simulation-based Autonomous Vehicle Verification}
% \author[1,3]{Abanoub Ghobrial\thanks{$^{1}${\footnotesize \{abanoub.ghobrial, greg.chance, kevin.mcareavey, kerstin.eder\}@bristol.ac.uk}}}
% \author[1,3]{Greg Chance}
% \author[1,3]{Kevin McAreavey}
% \author[2,3]{Severin Lemaignan\thanks{$^{2}${\footnotesize \{severin.lemaignan, tony.pipe\}@brl.ac.uk}}}
% \author[2,3]{Tony Pipe}
% \author[1,3]{Kerstin Eder}
% \affil[1]{Trustworthy Systems Laboratory, University of Bristol, Bristol, UK}
% \affil[2]{University of West of England, Bristol, UK}
% \affil[3]{Bristol Robotics Laboratory, Bristol, UK}

% \author{Abanoub Ghobrial\thanks{$^{1}${\footnotesize \{abanoub.ghobrial, greg.chance, kevin.mcareavey, kerstin.eder\}@bristol.ac.uk}}}
% \author{Greg Chance}
% \author{Kevin McAreavey}
% \author{Severin Lemaignan\thanks{$^{2}${\footnotesize \{severin.lemaignan, tony.pipe\}@brl.ac.uk}}}
% \author{Tony Pipe}

\author{Abanoub Ghobrial, Greg Chance, Kevin McAreavey, Severin Lemaignan, Tony Pipe, Kerstin Eder 
\thanks{{\footnotesize
Manuscript  
received ...;
revised ...;  
accepted.... 
Date of publication ...;
date of current version ....

This research has in part been funded by the ROBOPILOT and CAPRI projects. Both projects are part-funded by the Centre for Connected and Autonomous Vehicles (CCAV), delivered in partnership with Innovate UK under grant numbers 103703 (CAPRI) and 103288 (ROBOPILOT), respectively.
The Associate Editor for this paper was ....(\textit{Corresponding author: Abanoub Ghobrial.})

A.Ghobrial (e-mail: abanoub.ghobrial@bristol.ac.uk), 
G.Chance (e-mail: greg.chance@bristol.ac.uk), 
K.McAreavey (e-mail: kevin.mcareavey@bristol.ac.uk), 
and 
K.Eder (e-mail: kerstin.eder@bristol.ac.uk) 
are with the Trustworthy Systems Lab, Department of Computer Science, University of Bristol, Merchant Ventures Building, Woodland Road,  Bristol, BS8 1UQ, United Kingdom.

S.Lemaignan (e-mail: severin.lemaignan@brl.ac.uk)
and
T.Pipe (e-mail: tony.pipe@brl.ac.uk), 
are with the Bristol Robotics Lab, T Block, University of the West of England,Frenchay, Coldharbour Ln, Bristol, BS34 8QZ, United Kingdom.

Digital Object Identifier ....
}}}
% \affil{Trustworthy Systems Laboratory, University of Bristol, Bristol, UK}
% \affil{University of West of England, Bristol, UK}
% \affil{Bristol Robotics Laboratory, Bristol, UK}
%
\markboth{IEEE TRANSACTIONS ON INTELLIGENT TRANSPORTATION SYSTEMS VOL. ..., NO. ..., date...}{Ghobrial \MakeLowercase{\textit{et al.}}: On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification}
%
\maketitle
%
\begin{abstract}
\noindent 
Game engines are increasingly used as simulation platforms by the autonomous vehicle (AV) community to develop vehicle control systems and test environments.
%
A key requirement for simulation-based development and verification is determinism.
%
Whereby, a deterministic process will always produce the same output given the same initial conditions and event history.
%
Thus, making tests repeatable and yielding simulation results that are trustworthy and straightforward to debug.
%
However, game engines are seldom deterministic.

@@

% ***************************************************
%  FUNDING, REFS
% ***************************************************
% \section*{Acknowledgements}
% This research has in part been funded by the ROBOPILOT and CAPRI projects. Both
% projects are part-funded by the Centre for Connected and Autonomous
% Vehicles (CCAV), delivered in partnership with Innovate UK under grant numbers
% 103703 (CAPRI) and 103288 (ROBOPILOT), respectively.
\printbibliography
